---
title: "date_map homework"
author: "Ronan Tanona"
date: "2025-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(purrr)
library(dplyr)
```


##Exercise 1: Advanced Date Manipulation with lubridate
Generate a sequence of dates from January 1, 2015 to December 31, 2025, spaced by every two months. Extract the year, quarter, and ISO week number for each date.
```{r exercise1}
dates <- seq.Date(from = as.Date("2015-01-01"), 
                  to = as.Date("2025-12-31"), 
                  by = "2 months")
map_dfc(dates, ~ data.frame(
  date = .x,
  year = year(.x),
  quarter = quarter(.x),
  iso_week = isoweek(.x)
)) -> result1
```

Explanation: Here I used created a sequence of dates as required using seq.Date, saving that value sequence to then use in the map_dfc() command. Then, in mapping this sequence with map_dfc(), I pulled the year, quarter, and iso week as required.


##Exercise 3: Higher-Order Functions with purrr
Using map() and map_dbl(), compute the mean, median, and standard deviation for each numeric vector in the following list:
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))
```{r exercise3}
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))
map(num_lists, mean)
map_dbl(num_lists, mean)
map(num_lists, median)
map_dbl(num_lists, median)
map(num_lists, sd)
map_dbl(num_lists, sd)
```
This was pretty straight forward, as I was able to use the map() and map_dbl() commands for each set of information we wanted to pull. They each return them in different forms-- either lists or double vector

##Exercise 4:
